Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
moved a tikz figure to ipe figures/NumberOfBuildings.pdf
integrated two figures in case study into one

A way to achieve continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
a straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations. When the number 
of line features is different in the start and goal maps, a continuous 
selection is required and \citet{Chimani2014_Eat} proposed to generate a 
selection sequence applicable for road network.
They removed one road at each step while keeping the remaining roads connected.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregating original buildings in the same group by adding 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

@@

%At any time $t$, some of the bridges are picked to aggregate buildings 
%which grow to become too close.
%The buildings and the bridges already comprise some MSTs.

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings may change because 
%		of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

@@

\subsection{Eliminating small buildings}
\label{sec:Eliminate}
Following the previous steps of continuous generalization may result in the 
creation of small isolated building aggregates that do not belong to the goal 
map polygon because of their isolation.
That is why we eliminate a building aggregate if the area of this building is 
smaller than a threshold.
Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
we set this threshold as $a=0.16\,\mathrm{mm}^2$ on map.
The real threshold at time $t$ is
\[
a_t=a\cdot M_t^2.
\]
For a group of buildings that will be aggregated into one built-up area at time 
$t=1$, we consider the area sum of all the buildings at any time $t$, 
instead of considering each building individually.

@@

%\subsection{Running time analysis}
%Although a version with a 
%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
%version.

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of \citet{Johnson2014}.
The offsetting function is used for the buffering, dilation, erodion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale $1:50{,}000$.
This dataset was basically obtained from the data at scale $1:15{,}000$ 
by buffering with distance $25\,\mathrm{m}$,
where sometimes distance $50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than $100\,\mathrm{m}$.

@@

We set our goal scale at $1:50{,}000$, which means $M_\mathrm{g}=50{,}000$,
and $d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where $l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
according to our settings.
As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left when we simplified using
the Douglas--Peucker algorithm.

\begin{figure*}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Bridged original buildings 
		and goal shapes of the built-up areas (without removing small holes), 
		at scale $1:50{,}000$.
		There are $56$ built-up areas, which have $1{,}102$ edges in total.
		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
		for the region marked by the dashed circle.
	}
	\label{fig:GoalShape}
\end{figure*}

We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
This production costs $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:BuilidngNumber}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where $n_s=2{,}590$ is the number of buildings on start map
and $n_t$ is the number of buildings on a map at scale $1:M_t$.
According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure*}[tb]
	\centering
	\includegraphics{ContinuousGeneralization}
	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
		for the region marked in \fig\ref{fig:GoalShape}.
	}
	\label{fig:ContinuousGeneralization}
\end{figure*}

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data at scale $1:50{,}000$.
No small building is removed in our result or the existing data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{A comparison of our result and the existing data at scale 
		$1:50{,}000$.
		The brighter gray polygons represent the original buildings.
		The darker gray polygons are our result at time $t=1$.
		The gray polylines represent the data of the built-up areas at scale 
		$1:50{,}000$ from IGN, where some built-up areas are split because some 
		streets cross these areas.
	}
	\label{fig:ExperimentalComparison}
\end{figure*}

@@

We proposed a method to continuously generalize buildings to built-up areas
by aggregating and growing.
We managed to produce a sequence of maps 
in which the buildings are always growing and, at the same time, are simplified.
For the goal map at scale $1:50{,}000$,
the shapes of our built-up areas are more reasonable than the data from IGN.

>>>>

A way to achieve continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{Noellenburg2008}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
a straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations. When the number 
of line features is different in the start and goal maps, a continuous 
selection is required and \citet{Chimani2014_Eat} proposed to generate a 
selection sequence applicable for road network.
They removed one road at each step while keeping the remaining roads connected.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{GrowAndBridge}
	\caption{Aggregating original buildings in the same group by adding 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure}

@@

%At any time $t$, some of the bridges are picked to aggregate 
%buildings 
%which grow to become too close.
%The buildings and the bridges already comprise some MSTs.

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least 
%$d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other 
%parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than 
%$d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings may change because 
%		of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

@@

\subsection{Eliminating small buildings}
\label{sec:Eliminate}
Following the previous steps of continuous generalization may result in the 
creation of small isolated building aggregates that do not belong to the goal 
map polygon because of their isolation.
That is why we eliminate a building aggregate if its area is 
smaller than a threshold.
Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
we set this threshold as $a=0.16\,\mathrm{mm}^2$ on map.
The real threshold at time $t$ is
\[
a_t=a\cdot M_t^2.
\]
For a group of buildings that will be aggregated into one built-up area at time 
$t=1$, we consider the area sum of all the buildings at any time $t$, 
instead of considering each building individually.

@@

\subsection{Running time}

Although a version with a 
lower running time exists \citep[see][]{Chan1992}, we 
implemented the basic 
version.

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of 
\citet{Johnson2014}, which is based on the clipping algorithm of
\citet{Vatti1992Clip}.
The offsetting function is used for the buffering, dilation, 
erosion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under~64-bit 
Windows~7 on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scal~$1:15{,}000$, 
which means~$M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale~$1:50{,}000$.
This dataset was basically obtained 
from the data at scale~$1:15{,}000$ 
by buffering with distance~$25\,\mathrm{m}$,
where sometimes distance~$50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than~$100\,\mathrm{m}$.

@@

We set our goal scale at~$1:50{,}000$, 
which means~$M_\mathrm{g}=50{,}000$,
and~$d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where~$l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
according to our settings.
As a result~$\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where~$\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

Our program took~$93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:ExperimentalComparison} shows the bridged buildings 
and the goal shapes.
The~$56$ built-up areas have~$2{,}095$ edges before line 
simplification.
Using the Imai--Iri algorithm, we have~$1{,}102$ edges left.
In comparison, there are~$1{,}597$ edges left when we simplified 
using
the Douglas--Peucker algorithm.

%\begin{figure*}[tb]
%	\centering
%	\includegraphics{GoalShape}
%	\caption{Bridged original buildings 
%		and goal shapes of the built-up areas (without removing 
%small holes), 
%		at scale~$1:50{,}000$.
%		There are~$56$ built-up areas, which have~$1{,}102$ 
%		edges in total.
%		We show a sequence of maps in 
%\fig\ref{fig:ContinuousGeneralization} 
%		for the region marked by the dashed circle.
%	}
%	\label{fig:GoalShape}
%\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{Bridged original buildings,
		goal shapes at scale~$1:50{,}000$ (darker polygons), 
		and the built-up areas at scale~$1:50{,}000$ 
		from IGN (transparent polygons).
		Some built-up areas from IGN are split 
		because of streets' crossing.
		There are~$56$ goal shapes, which have~$1{,}135$ 
		edges in total.
		We show a sequence of maps in 
		\fig\ref{fig:ContinuousGeneralization} 
		for the region marked by the dashed circle.
	}
	\label{fig:ExperimentalComparison}
\end{figure*}

We produced a sequence of~$10$ maps,
i.e.,~$t \in \{0.1, 0.2, \dots, 1\}$.
This production costs~$668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:ExperimentalComparison}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:NumberOfBuildings}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} 
we used~$C_\mathrm{b2}$ and~$C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where~$n_s=2{,}590$ is the number of buildings on start map
and~$n_t$ is the number of buildings on a map at scale~$1:M_t$.
According to \fig\ref{fig:NumberOfBuildings}, 
our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure*}[tb]
	\centering
	\includegraphics{ContinuousGeneralization}
	\caption{A sequence of maps at time~$t \in \{0, 0.1, 0.2, 
	\dots, 1\}$
		for the region marked in 
		\fig\ref{fig:ExperimentalComparison}.
	}
	\label{fig:ContinuousGeneralization}
\end{figure*}

\begin{figure}[tb]
	\centering
	\includegraphics{NumberOfBuildings}
	\caption{A comparison of the numbers of building between our 
results and 
		T\"opfer's radical law.}
	\label{fig:NumberOfBuildings}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data at scale~$1:50{,}000$.
No small building is removed in our result or the existing data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have~$1{,}135$ edges while the data has~$4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

%\begin{figure*}[tb]
%	\centering
%	\includegraphics{ExperimentalComparison}
%	\caption{A comparison of our result and 
%		the existing data at scale~$1:50{,}000$.
%		The brighter gray polygons represent the original 
%buildings.
%		The darker gray polygons are our result at time~$t=1$.
%		The gray polylines represent the data of the built-up 
%		areas at scale~$1:50{,}000$ from IGN, 
%		where some built-up areas are split 
%		because some streets cross these areas.
%	}
%	\label{fig:ExperimentalComparison}
%\end{figure*}

@@

We proposed a method to continuously generalize buildings to built-up areas
by aggregating and growing.
We managed to produce a sequence of maps 
in which the buildings are always growing and, at the same time, are simplified.
For the goal map at scale~$1:50{,}000$,
the shapes of our built-up areas are more reasonable than the data from IGN.
